{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
Small corrections

	\subsection{Approximation and Smoothing via Basis Truncation}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$ to fit an completely unbiased estimate. This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. On the other hand, the important information on the curves could be missed with a too-small number of basis functions. This discussion is subject to the Bias-Variance Tradeoff and challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, do not introduce to much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error. The number $L$ can be chosen subjectively, but also trough the application of a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or another criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is subject of the simulation study.

>>>>

	\subsection{Approximation and Smoothing via Basis Truncation}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $\phi_{j \in \mathcal{I}}$ to fit an completely unbiased estimate. This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. On the other hand, the important information on the curves could be missed with a too-small number of basis functions. In that sense, this discussion is subject to the Bias-Variance Tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.
